Large Linear Multi-output Gaussian Process Learning

### 2017-04-11 paper/paper.tex
updated paper with re-run benchmarks
Minor paper touch-up / removed TODOs

Although this is a method of optimizing the marginal log likelihood, it can easily be augmented with a hyperprior $\log p(\bsth)$ term to Eq.~\ref{datall}.% what does "augmented with a hyperprior $\log p(\bsth)$ term to Eq.~\ref{datall}" mean? make this explicit here. a log probabliity is not a hyper prior (generally)

@@

\section{Results} % TODO read these over
\label{sec:results}
We evaluate the methods on held out data by using standardized mean square error (SMSE) of the test points with the predicted mean, and the negative log predictive density (NLPD) of the Gaussian likelihood of the inferred model. Notably, NLPD takes confidence into account, while SMSE only evaluates the mean prediction. In both cases, lower values represent better performance.

@@

The data used in this example are from 2007, and include $n=3,054$ training points and $150$ test points. The test points include 50 contiguous points extracted from each of the CAD, JPY, and AUD exchanges.

@@

\bibliography{paper}
\bibliographystyle{icml2017} % TODO - follow blei notes for this

>>>>

Although Eq.~\ref{datall} does not have a hyperprior $\log p(\bsth)$ term, it can easily be augmented with one.

@@

\section{Results}
\label{sec:results}
We evaluate the methods on held out data by using standardized mean square error (SMSE) of the test points with the predicted mean, and the negative log predictive density (NLPD) of the Gaussian likelihood of the inferred model. Notably, NLPD takes confidence into account, while SMSE only evaluates the mean prediction. In both cases, lower values represent better performance.

@@

The data used in this example are from 2007, and include $n=3054$ training points and $150$ test points. The test points include 50 contiguous points extracted from each of the CAD, JPY, and AUD exchanges.

@@

\bibliography{paper}
\bibliographystyle{icml2017}
